Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ \smaller \textbf{{Shanghai version \YellowPaperVersionNumber}}

### 2024-07-01 Paper.tex

\subsection{Post-Paris Updates}
Because the Beacon Chain generate a new slot every 12 seconds, post-\textit{Paris} updates can be scheduled to occur at a specific timestamp.
At the execution layer, the update will then happen in the first produced block after the scheduled timestamp.
For example the \textit{Shanghai} hard fork was scheduled to occur at 2023-04-12 10:27:35 UTC, on Epoch 194,048.
Validators failed to propose a block during the two first slots of this Epoch, but at slot 6,209,538 a validator finally proposed a the block 17,034,870, marking the transition to \textit{Shanghai} on the execution layer.

@@

&&&& Its behavior might be subject to change in an upcoming update. \\

>>>>

\subsection{Post-Paris Updates}
Because the Beacon Chain generate a new slot every 12 seconds, post-\textit{Paris} updates can be scheduled to occur at a specific timestamp.
At the execution layer, the update will then happen in the first produced block after the scheduled timestamp.
For example the \textit{Shanghai} hard fork was scheduled to occur at 2023-04-12 10:27:35 UTC, on Epoch 194,048.
Validators failed to propose a block during the two first slots of this Epoch, but at slot 6,209,538 a validator finally proposed the block 17,034,870, marking the transition to \textit{Shanghai} on the execution layer.

@@

&&&& Its behavior might be subject to breaking change in an upcoming update. \\
